---
title: "master-russian-word-length"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{master-russian-word-length}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(masterrussian)
library(magrittr)
```

# Setup

This vignette helps analysing the [1000 most common words](http://masterrussian.com/vocabulary/most_common_words.htm) from the masterrussian site.

```{r}
words <-
  words %>% add_russian_word_length()

head(words)
```

# How long are the most common words?

```{r}
words %>% 
  histogram_word_length()
```

As you can see the numbers of characters which occurs the most is 7. If we focus only on those words with 7 or less characters, we can already cover 3/4 of the 1000 most common words.

```{r}
cum_word_length(words, 7)
```

This is just about 4000 characters which seems very feasible.If you learn just a bit more than 10 characters per day, you could do this in about a year.

# Create training schedule

I think I can do about 100 characters per day. This would mean 3/4 of the most common words can be covered in 40 days.

```{r}
words %>% write_word_length_group()
```


